Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and music aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-13 figures/neural networks/Back_propagation.tex
Updates from Overleaf

		\draw[->,red,line width=0.05cm] (2,-0.25) -- (0.75,0.3);
		\draw[->,red,line width=0.05cm] (2,2) -- (0.75,1.6);
    	\end{tikzpicture}
	\caption[Backpropagation of errors through the network.]{Once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backwards.}.
	\label{fig:error-backpropagation}
\end{SCfigure}

>>>>

		\draw[->,red,line width=0.05cm] (2,-0.25) -- (0.75,0.3);
		\draw[->,red,line width=0.05cm] (2,2) -- (0.75,1.6);
    	\end{tikzpicture}
	\caption[Backpropagation of errors through the network.]{\small{Once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backwards.}}.
	\label{fig:error-backpropagation}
\end{SCfigure}

### 2023-04-13 figures/neural networks/Network_graph.tex
Updates from Overleaf

\begin{SCfigure}[12][h]
	\centering
    \begin{tikzpicture}[shorten >=1pt]
        \tikzstyle{unit}=[draw,shape=circle,minimum size=1.15cm]

@@

        \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (-0.5,4) -- (0.75,4) node [black,midway,yshift=+0.6cm]{input layer};
        \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (3.5,3) -- (4.75,3) node [black,midway,yshift=+0.6cm]{output layer};
    \end{tikzpicture}
    \caption[Network graph of a perceptron with $D$ input units and $C$ output units.]{The perceptron consists of $D$ input units and $C$ output units. All units are labeled according to their output: $y_i = f(z_i)$ in the case of output units; $x_i$ in the case of input units. The input values $x_i$ are propagated to each output unit using the weighted sum propagation rule. The additional input value $x_0 := 1$ is used to include the biases as weights.}
    \label{fig:perceptron}
\end{SCfigure}

>>>>

\begin{SCfigure}[12][ht]
	\centering
    \begin{tikzpicture}[shorten >=1pt]
        \tikzstyle{unit}=[draw,shape=circle,minimum size=1.15cm]

@@

        \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (-0.5,4) -- (0.75,4) node [black,midway,yshift=+0.6cm]{input layer};
        \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (3.5,3) -- (4.75,3) node [black,midway,yshift=+0.6cm]{output layer};
    \end{tikzpicture}
    \caption[Network graph of a perceptron with $D$ input units and $C$ output units.]{\small{The perceptron consists of $D$ input units and $C$ output units. All units are labeled according to their output: $y_i = f(z_i)$ in the case of output units; $x_i$ in the case of input units. The input values $x_i$ are propagated to each output unit using the weighted sum propagation rule. The additional input value $x_0 := 1$ is used to include the biases as weights.}}
    \label{fig:perceptron}
\end{SCfigure}

### 2023-04-13 figures/neural networks/Single Neuron.tex
Updates from Overleaf

		\draw (0,2.5) node[xshift=-10]{$w_0$} -- (p);
		\draw (0,1.75) node[xshift=-10]{$x_1$} --(p);
		\draw (0,0) node[xshift=-10]{$x_D$} -- (p);
		\draw (p) -- (3,1) node[xshift=30]{$y := f(z)$};
	\end{tikzpicture}
	\caption[Single processing units and its components.]{Single processing unit and its components. The activation function is denoted by $f$ and applied to the actual input $z$ of the unit to form its output $y = f(z)$. $x_1, \ldots, x_D$ represent input from other units within the network; $w_0$ is called bias and represents an external input to the unit. All inputs are mapped onto the actual input $z$ using the propagation rule.~\cite{Stutz2022}}
	\label{fig:processing-unit}
\end{SCfigure}

>>>>

		\draw (0,2.5) node[xshift=-10]{$w_0$} -- (p);
		\draw (0,1.75) node[xshift=-10]{$x_1$} --(p);
		\draw (0,0) node[xshift=-10]{$x_D$} -- (p);
		\draw (p) -- (3,1) node[xshift=30]{$y := a(z)$};
	\end{tikzpicture}
	\caption[Single processing units and its components.]{\small{Single processing unit and its components. The activation function is denoted by $a$ and applied to the actual input $z$ of the unit to form its output $y = a(z)$. $x_1, \ldots, x_D$ represent input from other units within the network; $w_0$ is called bias and represents an external input to the unit. The propagation rule maps all inputs onto the actual input $z$.}}
	\label{fig:processing-unit}
\end{SCfigure}

### 2023-04-13 figures/neural networks/Single_CNN.tex
Updates from Overleaf

\begin{SCfigure}[2\sidecaptionrelwidth][h]
	\centering
	\begin{tikzpicture}
		\node at (1.5,4){\begin{tabular}{c}input data\\or input feature map\end{tabular}};

@@

		\draw[fill=black,opacity=0.2,draw=black] (5.5,1.5) -- (7.5,1.5) -- (7.5,3.5) -- (5.5,3.5) -- (5.5,1.5);
		\draw[fill=black,opacity=0.2,draw=black] (5,1) -- (7,1) -- (7,3) -- (5,3) -- (5,1);
		\draw[fill=black,opacity=0.2,draw=black] (4.5,0.5) -- (6.5,0.5) -- (6.5,2.5) -- (4.5,2.5) -- (4.5,0.5);
		\draw[fill=black,opacity=0.2,draw=black] (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,0);
	\end{tikzpicture}
	\caption[Illustration of a convolutional layer.]{Illustration of a single convolutional layer. If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters to yield the output feature maps of layer $l$.}
	\label{fig:convolutional-layer}
\end{SCfigure}

>>>>

\begin{SCfigure}[2\sidecaptionrelwidth][h]
	\centering
        \scalebox{0.8}{
	\begin{tikzpicture}
		\node at (1.5,4){\begin{tabular}{c}input data\\or input feature map\end{tabular}};

@@

		\draw[fill=black,opacity=0.2,draw=black] (5.5,1.5) -- (7.5,1.5) -- (7.5,3.5) -- (5.5,3.5) -- (5.5,1.5);
		\draw[fill=black,opacity=0.2,draw=black] (5,1) -- (7,1) -- (7,3) -- (5,3) -- (5,1);
		\draw[fill=black,opacity=0.2,draw=black] (4.5,0.5) -- (6.5,0.5) -- (6.5,2.5) -- (4.5,2.5) -- (4.5,0.5);
		\draw[fill=black,opacity=0.2,draw=black] (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,0);
	\end{tikzpicture}
        }
	\caption[Illustration of a 2D convolutional layer.]{\small{Illustration of a 2D single convolutional layer. If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters (or kernels) to yield the output feature maps of layer $l$.}}
	\label{fig: convolutional layer}
\end{SCfigure}

### 2023-04-13 introduction/Subsections/Assumptions.tex
Updates from Overleaf

This thesis argues that high-level musical concepts are invariant to the unique tonal quality of the waveform, much like a sheet music composition can be performed in countless ways using various instruments and styles while retaining its essence.

High-level features like melody, harmony, rhythm, tempo, form, and expression are more abstract and can be recognized regardless of waveform or production style. This approach provides an objective and comprehensive perspective on a piece's musical content and meaning, similar to how reading sheet music reveals a piece's underlying structure and intention.

While a waveform may have a limited number of sheet music representations that accurately capture its musical elements, one sheet music composition can be performed in infinite ways using different instruments, voices, tempos, and interpretations. The unique tonal quality of a waveform is strongly influenced by the specific instrument or production technology used to create it, making it difficult to transcribe its sonic properties into precise sheet music notation.

Additionally, this unique tonal quality is represented by high-level natural language concepts that belong to a rich cultural and sociological tradition.

>>>>

This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, and others. This is akin to a sheet music composition being performed in myriad ways using diverse instruments and styles while preserving its core essence.

Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style. This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.

Although a waveform might have a limited number of sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations. The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.

Moreover, this distinct tonal quality is represented by high-level natural language concepts embedded within a rich cultural and sociological tradition.

### 2023-04-13 introduction/Subsections/Introduction.tex
Updates from Overleaf

It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to proper sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.

The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study. Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}, yet remains a vast open challenge.

>>>>

\subsubsection{Bridging the gap}

It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks for the symbolic domain \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to good sheet music "human" syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.

The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study. Bridging the gap between human perception \cite{Large1994ResonanceMeter}\cite{Thaut2014HumanPatter}, environmental and cultural factors \cite{Sears2014PerceivingCadence}, and computational solutions to mimic the formers \cite{Mullensiefen2003MeasuringJudgments} is an already tackled topic \cite{Hernandez-Olivan2023SymbolicMethods}, yet remains a vast open challenge.

### 2023-04-13 introduction/Subsections/Motivation.tex
Updates from Overleaf

Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure. It analyzes features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries. In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background. They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.

@@

Mesostructures \cite{Mesostructures2023} are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure. Examples of mesostructures include melody, arpeggios, syncopation, polyphonic grouping, and textural contrast. The article notes that mesostructures have received limited attention in deep learning, as current models only focus on microstructures. The article proposes a new approach to mesostructural audio modeling, which involves a differentiable arpeggiator and time-frequency scattering. The article also discusses the need for a time-invariant and multiscale differentiable time-frequency model of similarity at the level of both local spectra and spectrotemporal modulations.

>>>>

@@

Mesostructures \cite{Mesostructures2023} are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure. Examples of mesostructures include melody, arpeggios, syncopation, polyphonic grouping, and textural contrast. The article notes that mesostructures have received limited attention in deep learning, as current models only focus on microstructures. The article proposes a new approach to mesostructural audio modeling, which involves a differentiable arpeggiator and time-frequency scattering. The report also discusses the need for a time-invariant and multiscale differentiable time-frequency model of similarity at the level of both local spectra and spectrotemporal modulations.

\subsection{Sample MIR task}

Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure. It explores features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries. In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background. They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.

### 2023-04-13 introduction/Subsections/Objectives.tex
Updates from Overleaf

This work aims to uncover a generalization of the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks. Understanding how music is organized and composed is critical, and music theory plays a vital role.

@@

Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, and critical, holistic elements) and the production aspects. The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two aspects. Formally, our objective is to learn the embedding function $e(M)$ such that:

@@

%%%%%%%%%%%%%%%%%%%%%%%%
%POTENTIAL APPLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

This work aims to uncover a generalization of the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.

@@

Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, critical, holistic elements) and the production aspects. The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two elements. Formally, our objective is to learn the embedding function $e(M)$ such that:

@@

\subsection{Applications}
%%%%%%%%%%%%%%%%%%%%%%%%
%POTENTIAL APPLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-04-13 methods/subsections/experiment setup and hyperparameter tuning.tex
Updates from Overleaf

For finetuning and improving the model's behavior, we followed \href{http://karpathy.github.io/2019/04/25/recipe/}{\textit{A Recipe for Training Neural Networks}} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by \href{https://karpathy.ai/}{Andrej Karpathy} \cite{AndrejKarpathyHttps://karpathy.ai/}. A blog post that discusses a recipe for training neural networks. The author of the blog post tweeted about common mistakes people make when training neural nets and the post aims to expand on those mistakes by explaining how to avoid them through a particular process. Andrej Karpathy notes that there is often a gap between understanding the technical aspects of a neural network and achieving state-of-the-art results.

>>>>

For finetuning and improving the model's behavior, we followed \href{http://karpathy.github.io/2019/04/25/recipe/}{\textit{A Recipe for Training Neural Networks}} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by \href{https://karpathy.ai/}{Andrej Karpathy} \cite{AndrejKarpathyHttps://karpathy.ai/}. A blog post that discusses a recipe for training neural networks. The author of the blog aims to expand on common mistakes people make when training neural nets by explaining how to avoid them through a particular process. Andrej Karpathy notes that there is often a gap between understanding the technical aspects of a neural network and achieving state-of-the-art results.

\input{figures/neural networks/dropout}

### 2023-04-13 methods/subsections/machine learning.tex
Updates from Overleaf

@@

\input{figures/neural networks/convolution}

\item \textbf{Pooling layers:} These layers downsample the data, reducing the spatial or temporal dimensions of the input while retaining important information. A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix. This operation effectively reduces the input's dimensions while retaining the most essential information in each region.
\vspace*{3mm}

\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features learned in the previous layers. Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix. The nonlinearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
\vspace*{3mm}

@@

%CNN
\input{figures/neural networks/CNN_diagram}

%Single CNN
\input{figures/neural networks/Single_CNN}

>>>>

Deep learning is a machine learning subfield that utilizes deep neural networks to learn hierarchical data representations automatically. These networks handle complex, high-dimensional data across domains such as computer vision and natural language processing. Their effectiveness stems from their nonlinear modeling capabilities and scalability with large datasets.

A core algorithm in deep learning is backpropagation which efficiently computes gradients of the loss function concerning the network's parameters. It involves a two-step process: (1) forward pass, where input data propagates through the network to generate predictions, and (2) backward pass, where the error between predictions and ground truth is calculated and propagated back through the network. This process updates the network's parameters using gradient descent, which minimizes the loss function and improves the model's performance.

@@

\input{figures/neural networks/convolution}
%Single CNN
\input{figures/neural networks/Single_CNN}

\item \textbf{Pooling layers:} These layers downsample the data, reducing the spatial or temporal dimensions of the input while retaining important information. A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix. This operation effectively reduces the input's dimensions while retaining the essential information in each area.
\vspace*{3mm}

\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers. Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix. The nonlinearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
\vspace*{3mm}

@@

%Colour CNN
\input{figures/neural networks/colour CNN}

### 2023-04-13 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

\section{Model architecture and training strategy}
Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months. This period referred to as the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening. As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic. Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge. This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in new information to fit pre-existing schemas and modifying existing schemas resulting from new information. In the context of learning, complex structures are based on simpler ones, and transfer of learning occurs when dynamic structures capable of generalization are created. \cite{audioselfsupsurvey}

@@

Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) to learn discriminative and valuable representations of music without relying on explicit labels. By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.

@@

\begin{enumerate}
\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
\end{enumerate}

@@

\begin{enumerate}
\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a known invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
\item Encourages feature extraction: CSSLMR promotes learning useful and discriminative features or representations
\end{enumerate}

@@

We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}. Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.

The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language. This is achieved using techniques such as time-stretching, pitch-shifting, and adding noise to the samples. By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.

On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture. This is achieved using random segment selection, time-domain filtering, and frequency-domain masking. The goal is to maintain the production texture of the samples while disrupting their underlying composition.

@@

>>>>

\section{Model architecture and training strategy}
Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months. This period, called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening. As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic. Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge. This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest news. In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created. \cite{audioselfsupsurvey}

@@

Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels. By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.

@@

\begin{enumerate}
\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, encouraging the model to produce similar representations for positive and dissimilar representations for antagonistic pairs.
\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
\end{enumerate}

@@

\begin{enumerate}
\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a general invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
\item Encourages feature extraction: CSSLMR promotes learning practical and discriminative representations.
\end{enumerate}

@@

We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}. Specifically, we aim to minimize the loss function between an anchor, a positive, and a negative sample by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.

@@

\subsection{Encoder}

\subsection{Data augmentation and transformation pipeline}
The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language. This is achieved using techniques such as time-stretching, pitch-shifting, and adding noise to the samples. By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.

On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture. This is achieved using random segment selection, time-domain filtering, and frequency-domain masking. The goal is to retain the texture production of the samples while disrupting their underlying composition.

\subsection{Loss function}

### 2023-04-13 preface/preface.tex
Updates from Overleaf

\addcontentsline{toc}{chapter}{Acknowledgement}
\begin{preface}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)

Music and science have always been my two greatest passions. When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating Music Information Retrieval (MIR) field. With the support and encouragement of my loved ones, I took a leap of faith and moved to Stockholm to embark on this exciting journey.

>>>>

%\addcontentsline{toc}{chapter}{Acknowledgement}
\begin{preface}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)

Music and science have always been my two greatest passions. When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating field of MIR from an industrial perspective. With the support and encouragement of my loved ones, I took a leap of faith and moved to Stockholm to embark on this exciting journey.
